R Notebook

### 2022-04-11 Code/Simulation.Rmd
deleted unnecessary code, fixed copula_only section

```{r}
# Load packages
library(xtable)
library(dgof)
library(tidyverse)
library(KSgeneral)
library(copula)
library(evd)
library(ismev)
source('tspb.R')
```

@@

```{r hist_rounded}
# Test to show that rounding changes the power of the test
test_rounded <- function(n_tests, n_samples, digits) {

  p_values <- double(n_tests)

  for(i in 1:n_tests) {

    # Generate random rounded data, perform a KS-test, and store the p-value
    data <- round(rnorm(n_samples), digits)
    p_values[i] <- ks.test(data, "pnorm")$p.value
  }

  return(p_values)
}

# Create the histograms displaying p-values from each test
n_tests <- 1000
n <- 100
hist1 <- suppressWarnings(test_rounded(n_tests, n, 2))
hist2 <- suppressWarnings(test_rounded(n_tests, n, 1))

# Create a master data_frame with all the results
histogram <- c(rep(".01", n_tests), rep(".1", n_tests))
p_values <- c(hist1, hist2)
results <- data_frame(p_values, histogram)

# Generate histograms plot
hist_rounded <- ggplot(results) + 
                geom_histogram(aes(x = p_values, fill = histogram), binwidth = 1/20, boundary = 0) + 
                facet_grid(~histogram) +
                theme(legend.position = "none") +
                scale_x_continuous(name = "p-value", breaks = seq(0, 1))

# Save the histogram figure
ggsave(filename = "hist_rounded.pdf", plot = hist_rounded, path = "../Manuscript", height = 2.1, width = 6)

qqplot(hist2, runif(100), xlab = "Rounded", ylab = "Uniform", main = "Testing qqplot")
abline(0, 1)
p <- ggplot(results, aes(sample = p_values))
p + stat_qq(distribution = stats::qunif) + geom_abline(intercept = 0, slope = 1) + xlim(0, 1) + ylim(0, 1)
```

```{r hist_general}
# Test the KSgeneral package as a solution to rounded data
test_general <- function(n_tests, n_samples, digits, B) {

  results1 <- double(n_tests)
  results2 <- double(n_tests)
  results3 <- double(n_tests)
  results4 <- double(n_tests)

  # Create the rounded normal step function
  left <- -4-0.1^digits
  y <- pnorm(seq(left, 4, by = 0.1^digits))
  sfun  <- stepfun(seq(-4, 4, by = 0.1^digits), y)

  for (i in 1:n_tests) {
    cat(i, "")
    # Generate random rounded data, perform 3 KS-tests, and store the p-values
    # 1. Using the rounded normal step function
    # 2. Using the naive continuous standard normal function
    data <- round(rnorm(n_samples), digits)
    results1[i] <- KSgeneral::disc_ks_test(data, sfun, exact = TRUE)$p.value
    results2[i] <- dgof::ks.test(data, sfun, exact = TRUE)$p.value
    results3[i] <- ks.test(data, sfun, simulate.p.value = TRUE, B = B)$p.value
    results4[i] <- ks.test(data, "pnorm")$p.value
  }

  # Create a master data_frame for p-values
  test <- c(rep("KSgeneral", n_tests), rep("dgof", n_tests), rep("dgofsim", n_tests), rep("Naive", n_tests))
  digits <- c(rep(.1^digits, 4*n_tests))
  p_values <- c(results1, results2, results3, results4)
  results <- data_frame(p_values, test, digits)

  return(results)
}

n_tests = 100
n = 30
B = 1000

# Create the histograms displaying p-values from each test
test1 <- suppressWarnings(test_general(n_tests, n, digits = 2, B = B))
test2 <- suppressWarnings(test_general(n_tests, n, digits = 1, B = B))
results <- rbind(test1, test2)

# Generate histograms plot
hist_general <- ggplot(results) + 
                geom_histogram(aes(x = p_values, fill = test), boundary = 0, binwidth = 1/20) + 
                scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                facet_grid(test~digits) +
                theme(legend.position = "none")

# Save the histogram figure
ggsave(filename = "hist_general.pdf", plot = hist_general, path = "../Manuscript", height = 4.2, width = 6)

proc.time() - ptm

qqplot(test1$p_values[1:100], runif(100), xlab = "KSGeneral", ylab = "Uniform", main = "Testing qqplot")
abline(0, 1)
# could try qqplot for unit interval
# is qqplot close to 45 degree line, otherwise no
```

@@

# Set variables
n <- 100
ar <- 0.5
counter <- 0
nrep <- 1
B <- 100

@@

>>>>

```{r}
# Load packages
library(dgof)
library(tidyverse)
library(copula)
library(evd)
library(ismev)
source('tspb.R')
```

@@

@@

# Super naive KS-test with fitted parameters
test_super_duper_naive <- function(x) {
  p.value <- ks.test(x, "pnorm", mean = 0, sd = 1)$p.value
  list(p.value = p.value)
}

@@

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_super_duper_naive(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n))$p.value)
